A Survey of Range-Only SLAM Techniques and Sensors

### 2018-11-05 Paper.tex
Minor fixes
Mostly changing the wording of the abstract and introduction paragraph to be more cohesive

	%The end of the abstract, I think, needs a better explanation of the survey other than stating that RO-SLAM techniques will be explored, ie: a more unifying theme
	\begin{abstract}		
		A common aspect in many autonomous robotics applications is addressing the problem of Simultaneous Localization and Mapping (SLAM). In most SLAM applications, the robot identifies distinguishable features in the environment, known as landmarks, through sensors such as cameras and laser rangefinders. Sensing these landmarks provide the robot with information such as range and bearing, which are used in the estimation processes of the robot's pose and the landmark locations within the map. However, some applications use landmarks which are only capable of providing range information, such as wireless and acoustic beacons. In this survey, the variety of techniques used to solve the SLAM problem with respect to range only sensors is explored.
	\end{abstract}

@@

		The Simultaneous Localization and Mapping (SLAM) problem is a common aspect of many robotics applications. SLAM involves estimating the pose of a mobile robot and building a map of its environment with no priori knowledge of said environment. The SLAM problem is a chicken-and-egg type problem, where the pose of the robot is ascertained with respect to a global frame, or map, and the building of a map requires knowledge of the robot's pose. There are many algorithms used to solve this problem, many use a landmark-based approach. Landmarks are distinguishable feature in an environment which can be observed via devices such as a camera or laser rangefinder. Said devices can be used to estimate the distance and orientation of the landmark relative to the robot. As the robot traverses the environment it continues to observe and collect landmarks. The sensed distance and orientation from each landmark is combined with odometry readings to get an refined estimation of the robot pose and map. 
		%It can continue observing that landmark, as well as collecting new landmarks, and using the sensed distances and angles combined with odometry readings to refine its estimation of the robot's pose and map. 
		In most SLAM applications, references to the map is synonymous with the locations and features of the landmarks.

>>>>

	%The end of the abstract, I think, needs a better explanation of the survey other than stating that RO-SLAM techniques will be explored, ie: a more unifying theme
	\begin{abstract}		
		A common aspect in many autonomous robotics applications is addressing the problem of Simultaneous Localization and Mapping (SLAM). In most SLAM applications, the robot identifies distinguishable features in the environment, known as landmarks, through sensors such as cameras and laser rangefinders. Sensing these landmarks provide the robot with information such as range and bearing to the landmark, which are used in various algorithms responsible for determining the robot's pose and the landmark locations within the map. However, some applications have the restriction of using landmarks which are only capable of providing range information, such as wireless and acoustic beacons. Attempting to simultaneously localize and map with this restriction is termed Range-Only Simultaneous Localization and Mapping (RO-SLAM). This paper examines recent advances in the algorithms and technologies utilized to accomplish RO-SLAM.

		% In this survey, the variety of techniques used to solve the SLAM problem with respect to range only sensors is explored.
	\end{abstract}

@@

		The task of Simultaneous Localization and Mapping (SLAM) is a common aspect in many robotics applications. SLAM involves estimating the pose of a robot while simultaneously building a map of its environment with no priori knowledge of said environment. This task can be represented as a causality dilemma, where the pose of the robot is ascertained with respect to a global frame, or map, and the creation of a map requires knowledge of the robot's pose. There are a variety algorithms used to solve this problem, many of which use a landmark-based approach. Landmarks are distinguishable feature in an environment which can be observed via devices such as a camera or laser rangefinder. Said devices can be used to measure propeties such as the distance or orientation of the landmark relative to the robot. As the robot traverses the environment it continues to observe and collect landmarks while simultaneously building a map and localizing itself within the map. The sensed distance and orientation from each landmark is combined with odometry readings to get an refined estimation of the robot pose and map. 
		%It can continue observing that landmark, as well as collecting new landmarks, and using the sensed distances and angles combined with odometry readings to refine its estimation of the robot's pose and map. 
		In most SLAM applications, references to the map is synonymous with the locations and features of the landmarks.
